---
title: "Data preparation"
bibliography: references.bib
link-citations: true
author: "Rob Franken"
output: 
  html_document:
    css: tweaks.css
    toc:  true
    toc_float: true
    number_sections: false
    toc_depth: 1
    code_folding: show
    code_download: yes
---

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test3"))
options(width = 100)
rgl::setupKnitr()

```


```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

Last compiled on `r format(Sys.time(), '%d-%m-%Y')`

---  

# Getting started

To copy the code, click the button in the upper right corner of the code-chunks.

## clean up

```{r, results='hide'}
rm(list=ls())
gc()
```

<br>


## general custom functions

- `fpackage.check`: Check if packages are installed (and install if not) in R
- `fsave`: Function to save data with time stamp in correct directory
- `fload`: Function to load R-objects under new names
- `fshowdf`: Print objects (`tibble` / `data.frame`) nicely on screen in `.Rmd`

```{r, fun}
fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

fsave <- function(x, file, location = "./data/processed/", ...) {
    if (!dir.exists(location))
        dir.create(location)
    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
    totalname <- paste(location, datename, file, sep = "")
    print(paste("SAVED: ", totalname, sep = ""))
    save(x, file = totalname)
}

fload  <- function(fileName){
  load(fileName)
  get(ls()[ls() != "fileName"])
}

fshowdf <- function(x, caption = NULL, digits = 2, footnote = NULL, ...) {
    knitr::kable(x, digits = digits, "html", caption = caption, ...) %>%
        kableExtra::footnote(general = footnote) %>%
        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
        kableExtra::scroll_box(width = "100%", height = "300px")
}
```


<br>

## necessary packages

- `tidyverse`: data wrangling

```{r, packages, message=FALSE, results='hide'}
packages = c("tidyverse")
fpackage.check(packages)
rm(packages)
```

<br>

<script>
function myFunction() {

            var btn = document.getElementById("myButton");
            //to make it fancier
            if (btn.value == "Click to hide code") {
                btn.value = "Show code";
                btn.innerHTML = "Show code";
            }
            else {
                btn.value = "Click to hide code";
                btn.innerHTML = "Hide code";
            }
            //this is what you're looking for
            var x = document.getElementById("myDIV");
            if (x.style.display === "none") {
                x.style.display = "block";
            } else {
                x.style.display = "none";
            }
        }
          
</script>


# Download data

The anonymized data-sets [@sportsfriendships] are deposited in DANS EASY. You can download the data-sets [here](https://ssh.datastations.nl/dataset.xhtml?persistentId=doi:10.17026/SS/GODKDR).

Download the data-files `short_public.R`, `alter_public.R`, and `data_public.R` and put them in the `./data/` folder. But first, make a `./data/` folder: 

```{r, eval=F}
ifelse(!dir.exists("data"), dir.create("data"), FALSE)
``` 

<br>

To see the code used to anonymize the raw data files, click the button below.

<button class=button1 onclick="myFunction()" id="myButton" value="Click To Open Instructions">Show code: from raw to public data</button>

<div style="display:none;" id="myDIV">
<br>

## load in raw data
```{r eval=FALSE}
# ego-survey
ego <- read.csv("./rawdata/results-survey429769.csv")

#alter survey
alter <- read.csv("./rawdata/results-survey659119.csv")
```

<br>

## make public data-set to deposit {.tabset .tabset-fade} 

```{r, eval=FALSE}
#first, remove 'fake'/test responses
#that is, with empty email string
#ego <- ego[-which(ego$email==""),]

#replace email with 'respnr'.
#some respondents have multiple (incomplete) responses.
ego$respnr <- NA

for (i in 1:nrow(ego)) {
  ego$respnr[i] <- which(unique(ego$email) %in% ego$email[i])
}

# we subset the combination of 'email' and 'respnr'...
merge <- ego[,c("email", "respnr")]
# remove duplicates
merge <- distinct(merge)

#so that we can replace email/identifier in the alter-data
alter <- merge(alter,merge, by="email")

#now we can remove names and email from both dataframes
ego <- select(ego, -email, -firstname, -lastname, -ipaddr)
alter <- select(alter, -email, -firstname, -lastname, -ipaddr)

fsave(ego, file="ego_public.RDa")
fsave(alter, file="alter_public.RDa")

load("./data/data_public.R")
fsave(x, file="data_public.RDa")
```

</div>

----

<br>

# Import data

- `short_public.R`: anonymized data of the additional ego-survey
- `alters_public.R`: anonymized data of the additional alter-survey
- `data_public.R`: anonymized data of alters nested in ego (with data on: ego, alter and dyad characteristics; constructed from the main survey data).


```{r, eval=FALSE}
ego <- fload("./data/short_public.Rda")
alter <- fload("./data/alters_public.Rda")
dat <- fload("./data/data_public.Rda")
#@RF hier nog closeness / contact freq. aan; o.b.v. voorgaande dataset?
```

--- 

<br>

# Wrangling

In case you don't wish to replicate the data-set, you may obtain it by downloading: `r xfun::embed_file("./data_shared/egonets.rda")`

## accuracy from ego's perspective

I calculate ego's accuracy in 'estimating' alters position on various items. I also attach variables at ego/alter level (gender age, education), dyad (duration); sameness; Relational functions (confidant, study, friend, sports)

```{r , eval=F}
#first, extract egos at least one of whose alters filled out the survey
ego <- ego[-which(!ego$respnr %in% unique(alter$respnr)),]

#i exported all ego responses, including those that were not completed,
#because a small number of egos did not 'submit' their answers, yet their alters filled out their part
ego <- ego[which(ego$lastpage>13),]

#make an (empty) dataframe to store output in, with a row for each alter of ego
df <- data.frame(respnr = alter$respnr,
                 dyad = NA,
                 tie = NA,
                 ego = "ego",
                 
                 #ego characteristics
                 ego_gender = NA,
                 ego_educ = NA,
                 ego_age = NA,
                 
                 #alter
                 alter_gender = NA,
                 alter_educ = NA,
                 alter_age = NA,
                 
                 #sameness
                 same_gender = NA,
                 same_educ = NA,
                 same_age = NA,
                 
                 #networks
                 cdn = NA,
                 study = NA,
                 bff = NA,
                 csn = NA, 
                 
                 #dyad
                 duration = NA,
                 
                 #structure
                 embeddedness = NA,
                 
                 #### opionions ######
                 
                 #left right placement
                 LR.self = NA,
                 LR.perception = NA,
                 LR.truth = NA,
                 LR.accuracy = NA,
                 
                 #importance of political themes
                 imp_crime.self = NA,
                 imp_crime.perception = NA, #crime
                 imp_crime.truth = NA,
                 imp_crime.accuracy = NA,
                 imp_climate.self = NA,
                 imp_climate.perception = NA, #climate
                 imp_climate.truth = NA,
                 imp_climate.accuracy = NA,
                 imp_discrim.self = NA,
                 imp_discrim.perception = NA, #discrimination 
                 imp_discrim.truth = NA,
                 imp_discrim.accuracy = NA,
                 imp_housing.self = NA,
                 imp_housing.perception = NA, #housing shortage
                 imp_housing.truth = NA,
                 imp_housing.accuracy = NA,
                 imp_refugee.self = NA,
                 imp_refugee.perception = NA, #refugees
                 imp_refugee.truth = NA,
                 imp_refugee.accuracy = NA,
          
                 #eco-friendly actions
                 sechand.self = NA,
                 sechand.perception = NA, #buying second hand products
                 sechand.truth = NA,
                 sechand.accuracy = NA,
                 replace.self = NA,
                 replace.perception = NA, #using items as long as possible before replacement
                 replace.truth = NA, 
                 replace.accuracy = NA,
                 animal.self = NA,
                 animal.perception = NA, #reduced consumption of animal products
                 animal.truth = NA, 
                 animal.accuracy = NA, 
                 
                 #climate policy
                 fly.self = NA,
                 fly.perception = NA, #flight tax
                 fly.truth = NA,
                 fly.accuracy = NA,
                 meat.self = NA,
                 meat.perception = NA, #meat tax
                 meat.truth = NA, 
                 meat.accuracy = NA,
                 nature.self = NA,
                 nature.perception = NA, #expandng nature reserves
                 nature.truth = NA, 
                 nature.accuracy = NA, 
                 
                 #migration (policy)
                 cap.self = NA,
                 cap.perception = NA, #annual cap on asylum seekers
                 cap.truth = NA,
                 cap.accuracy = NA,
                 student.self=NA,
                 student.perception = NA, #international students 'enrich' Dutch universities
                 student.truth = NA, 
                 student.accuracy = NA, 
                 threat.self = NA,
                 threat.perception = NA, #migration as a threat to Dutch culture
                 threat.truth = NA, 
                 threat.accuracy = NA)
                 
#reorder
df <- df[order(df$respnr),]
rownames(df) <- 1:nrow(df)

#recode answers on statements numerically
{
ego[ego=="Helemaal eens"] <- 4
ego[ego=="Eens"] <- 3
ego[ego=="Oneens"] <- 2
ego[ego=="Helemaal oneens"] <- 1
ego[ego=="Helemaal van toepassing"] <- 4
ego[ego=="Enigszins van toepassing"] <- 3
ego[ego=="Nauwelijks van toepassing"] <- 2
ego[ego=="Niet van toepassing"] <- 1
ego[ego=="Zeer belangrijk"] <- 4
ego[ego=="Belangrijk"] <- 3
ego[ego=="Niet belangrijk, maar ook niet onbelangrijk"] <- 2
ego[ego=="Niet belangrijk"] <- 1
alter[alter=="Helemaal eens"] <- 4
alter[alter=="Eens"] <- 3
alter[alter=="Oneens"] <- 2
alter[alter=="Helemaal oneens"] <- 1
alter[alter=="Helemaal van toepassing"] <- 4
alter[alter=="Enigszins van toepassing"] <- 3
alter[alter=="Nauwelijks van toepassing"] <- 2
alter[alter=="Niet van toepassing"] <- 1
alter[alter=="Zeer belangrijk"] <- 4
alter[alter=="Belangrijk"] <- 3
alter[alter=="Niet belangrijk, maar ook niet onbelangrijk"] <- 2
alter[alter=="Niet belangrijk"] <- 1
}

for (i in unique(df$respnr)) {
 
 ## unique(df$respnr)[7]->i

#  print(i)
  
  #get egodata corresponding to i
  egodata <- ego[which(ego$respnr==i),]

  #some double ego-responses (for those who did not complete, but did send the invitation to alters). I take the response that reached the latest page.
  egodata <- egodata[ which(egodata$lastpage == max(egodata$lastpage[!is.na(egodata$lastpage)])), ] 
  
  #get alterdata
  alterdata <- alter[which(alter$respnr==i),]

  #find out which of ego's alters (x and y) filled out the survey
  ind <- which(c(egodata$attribute_9, egodata$attribute_10) %in% alterdata$token)
  
  #get alter data of i
  data <- dat[which(dat$respnr==i),]
  
  #take the row(s) corresponding to the selected alter(s) that participated 
  data <- data[which(data$token %in% c(egodata$attribute_9, egodata$attribute_10)[ind]),]
  
  #give dyad id (i.e., ego-alter dyad of ego-alterx and ego-altery)
  df$dyad[which(df$respnr==i)] <-  as.numeric(c(paste0(1000 + df$respnr[which(df$respnr==i)][1], "1"), paste0(1000 + df$respnr[which(df$respnr==i)][1], "2")) )[ind]
  
  #also a tie id (giving direction); here, everything is from ego's perspective. I add a "1" to indicate this ("2") for alter perspective
  df$tie[which(df$respnr==i)] <- as.numeric(paste0(df$dyad[which(df$respnr==i)], "1"))
  
  #ego covars
  df$ego_gender[which(df$respnr==i)] <-  data$ego_gender[1]
  df$ego_educ[which(df$respnr==i)] <- data$ego_educ[1]
  df$ego_age[which(df$respnr==i)] <- data$ego_age[1]
  
  #alter
  df$alter_gender[which(df$respnr==i)] <- data$alter_gender
  df$alter_educ[which(df$respnr==i)] <- data$alter_educ
  df$alter_age[which(df$respnr==i)] <- data$alter_age
  
  #dyad
  df$duration[which(df$respnr==i)] <- data$duration
  #@RF. add closeness/frequency

  #same
  df$same_gender[which(df$respnr==i)] <- data$same_gender
  df$same_educ[which(df$respnr==i)] <- data$same_educ
  df$same_age[which(df$respnr==i)] <- data$same_age

  #network
  df$cdn[which(df$respnr==i)] <- data$cdn
  df$study[which(df$respnr==i)] <- data$study
  df$bff[which(df$respnr==i)] <- data$bff
  df$csn[which(df$respnr==i)] <- data$csn
  
  ### embeddedness ###
  #n_tie / (n_tie + n_notie)
  
  #alterX
  tie <- length( which(c(egodata$adjacency.SQ001.,egodata$adjacency.SQ002.,egodata$adjacency.SQ003.,egodata$adjacency.SQ004.,egodata$adjacency.SQ005.,
                         egodata$adjacency.SQ006.,egodata$adjacency.SQ007.,egodata$adjacency.SQ008.,egodata$adjacency.SQ009.,egodata$adjacency.SQ010.,
                         egodata$adjacency.SQ011.,egodata$adjacency.SQ012.,egodata$adjacency.SQ013.,egodata$adjacency.SQ014.,egodata$adjacency.SQ015.,
                         egodata$adjacency.SQ016.,egodata$adjacency.SQ017.,egodata$adjacency.SQ018.,egodata$adjacency.SQ019.,egodata$adjacency.SQ020.)
                         =="Ja") )
                 
  notie <- length( which(c(egodata$adjacency.SQ001.,egodata$adjacency.SQ002.,egodata$adjacency.SQ003.,egodata$adjacency.SQ004.,
                           egodata$adjacency.SQ005.,egodata$adjacency.SQ006.,egodata$adjacency.SQ007.,egodata$adjacency.SQ008.,
                           egodata$adjacency.SQ009.,egodata$adjacency.SQ010.,egodata$adjacency.SQ011.,egodata$adjacency.SQ012.,
                           egodata$adjacency.SQ013.,egodata$adjacency.SQ014.,egodata$adjacency.SQ015.,egodata$adjacency.SQ016.,
                           egodata$adjacency.SQ017.,egodata$adjacency.SQ018.,egodata$adjacency.SQ019.,egodata$adjacency.SQ020.)=="Nee") )
    
  embedX <- tie/(tie+notie)

  #alterY
  tie <- length( which(c(egodata$adjacency2.SQ001.,egodata$adjacency2.SQ002.,egodata$adjacency2.SQ003.,egodata$adjacency2.SQ004.,
                         egodata$adjacency2.S005.,egodata$adjacency2.SQ006.,egodata$adjacency2.SQ007.,egodata$adjacency2.SQ008.,
                         egodata$adjacency2.SQ009.,egodata$adjacency2.SQ010.,egodata$adjacency2.SQ011.,egodata$adjacency2.SQ012.,
                         egodata$adjacency2.SQ013.,egodata$adjacency2.SQ014.,egodata$adjacency2.SQ015.,egodata$adjacency2.SQ016.,
                         egodata$adjacency2.SQ017.,egodata$adjacency2.SQ018.,egodata$adjacency2.SQ019.,egodata$adjacency2.SQ020.)
                         =="Ja") )
                 
  notie <- length( which(c(egodata$adjacency2.SQ001.,egodata$adjacency2.SQ002.,egodata$adjacency2.SQ003.,egodata$adjacency2.SQ004.,
                           egodata$adjacency2.SQ005.,egodata$adjacency2.SQ006.,egodata$adjacency2.SQ007.,egodata$adjacency2.SQ008.,
                           egodata$adjacency2.SQ009.,egodata$adjacency2.SQ010.,egodata$adjacency2.SQ011.,egodata$adjacency2.SQ012.,
                           egodata$adjacency2.SQ013.,egodata$adjacency2.SQ014.,egodata$adjacency2.SQ015.,egodata$adjacency2.SQ016.,
                           egodata$adjacency2.SQ017.,egodata$adjacency2.SQ018.,egodata$adjacency2.SQ019.,egodata$adjacency2.SQ020.)=="Nee") )
    
  embedY <- tie/(tie+notie)
  
  df$embeddedness[which(df$respnr==i)] <- c(embedX,embedY)[ind]

  #### ego's own position
  df$LR.self[which(df$respnr==i)] <- as.numeric(stringr::str_extract(egodata$P1, pattern = "\\(?[0-9,.]+\\)?"))
  df$imp_crime.self[which(df$respnr==i)] <- egodata$P2.SQ001.
  df$imp_climate.self[which(df$respnr==i)] <- egodata$P2.SQ002.
  df$imp_discrim.self[which(df$respnr==i)] <- egodata$P2.SQ003.
  df$imp_housing.self[which(df$respnr==i)] <- egodata$P2.SQ004.
  df$imp_refugee.self[which(df$respnr==i)] <- egodata$P2.SQ005.
  df$sechand.self[which(df$respnr==i)] <- egodata$C2.SQ001.
  df$replace.self[which(df$respnr==i)] <- egodata$C2.SQ002.
  df$animal.self[which(df$respnr==i)] <- egodata$C2.SQ003.
  df$fly.self[which(df$respnr==i)] <- egodata$C1.SQ001.
  df$meat.self[which(df$respnr==i)] <- egodata$C1.SQ002.
  df$nature.self[which(df$respnr==i)] <- egodata$C1.SQ003.
  df$cap.self[which(df$respnr==i)] <- egodata$M1.SQ001.
  df$student.self[which(df$respnr==i)] <- egodata$M1.SQ002.
  df$threat.self[which(df$respnr==i)] <- egodata$M1.SQ003.
  
  #### ego's perception of corresponding alters' positions
  
  #LR
  df$LR.perception[which(df$respnr==i)] <- 
    c(as.numeric(stringr::str_extract(egodata$P1X,pattern = "\\(?[0-9,.]+\\)?")),
      as.numeric(stringr::str_extract(egodata$P1Y,pattern = "\\(?[0-9,.]+\\)?")) )[ind]
  
  #importance of political topics
  df$imp_crime.perception[which(df$respnr==i)] <- c(egodata$P2X.SQ001.,egodata$P2Y.SQ001.)[ind]
  df$imp_climate.perception[which(df$respnr==i)] <- c(egodata$P2X.SQ002.,egodata$P2Y.SQ002.)[ind]
  df$imp_discrim.perception[which(df$respnr==i)] <- c(egodata$P2X.SQ003.,egodata$P2Y.SQ003.)[ind]
  df$imp_housing.perception[which(df$respnr==i)] <- c(egodata$P2X.SQ004.,egodata$P2Y.SQ004.)[ind]
  df$imp_refugee.perception[which(df$respnr==i)] <- c(egodata$P2X.SQ005.,egodata$P2Y.SQ005.)[ind]
  
  #eco-friendly behavior
  df$sechand.perception[which(df$respnr==i)] <- c(egodata$C2X.SQ001., egodata$C2Y.SQ001.)[ind] 
  df$replace.perception[which(df$respnr==i)] <- c(egodata$C2X.SQ002., egodata$C2Y.SQ002.)[ind] 
  df$animal.perception[which(df$respnr==i)] <- c(egodata$C2X.SQ003., egodata$C2Y.SQ003.)[ind] 
  
  #climate policy attitude
  df$fly.perception[which(df$respnr==i)] <- c(egodata$C1X.SQ001., egodata$C1Y.SQ001.)[ind] 
  df$meat.perception[which(df$respnr==i)] <- c(egodata$C1X.SQ002., egodata$C1Y.SQ002.)[ind] 
  df$nature.perception[which(df$respnr==i)] <- c(egodata$C1X.SQ003., egodata$C1Y.SQ003.)[ind] 
  
  #migration (policy) attitude
  df$cap.perception[which(df$respnr==i)] <- c(egodata$M1X.SQ001., egodata$M1Y.SQ001.)[ind]
  df$student.perception[which(df$respnr==i)] <- c(egodata$M1X.SQ002., egodata$M1Y.SQ002.)[ind]
  df$threat.perception[which(df$respnr==i)] <- c(egodata$M1X.SQ003., egodata$M1Y.SQ003.)[ind]

  #### where do(es) alter(s) place themselves?
  
  #LR
  
  df$LR.truth[which(df$respnr==i)]  <- c( ifelse( length (as.numeric(stringr::str_extract(alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$P1, pattern = "\\(?[0-9,.]+\\)?"))) == 0, NA, as.numeric(stringr::str_extract(alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$P1, pattern = "\\(?[0-9,.]+\\)?"))), ifelse( length (as.numeric(stringr::str_extract(alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$P1, pattern = "\\(?[0-9,.]+\\)?"))) == 0, NA, as.numeric(stringr::str_extract(alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$P1, pattern = "\\(?[0-9,.]+\\)?"))) )[ind]
  

  #importance of topics
  df$imp_crime.truth[which(df$respnr==i)] <- c( ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$P2.SQ001) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$P2.SQ001),  ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$P2.SQ001) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$P2.SQ001) )[ind]
  
  df$imp_climate.truth[which(df$respnr==i)] <- c( ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$P2.SQ002) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$P2.SQ002),  ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$P2.SQ002) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$P2.SQ002) )[ind]
  
  df$imp_discrim.truth[which(df$respnr==i)] <- c( ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$P2.SQ003) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$P2.SQ003),  ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$P2.SQ003) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$P2.SQ003) )[ind]

  df$imp_housing.truth[which(df$respnr==i)] <- c( ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$P2.SQ004) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$P2.SQ004),  ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$P2.SQ004) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$P2.SQ004) )[ind]
  
  df$imp_refugee.truth[which(df$respnr==i)] <- c( ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$P2.SQ005) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$P2.SQ005),  ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$P2.SQ005) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$P2.SQ005) )[ind]

 #eco-friendly actions
  df$sechand.truth[which(df$respnr==i)] <- c( ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$C2.SQ001) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$C2.SQ001),  ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$C2.SQ001) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$C2.SQ001) )[ind]
  
  df$replace.truth[which(df$respnr==i)] <-  c( ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$C2.SQ002) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$C2.SQ002),  ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$C2.SQ002) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$C2.SQ002) )[ind]
  
  df$animal.truth[which(df$respnr==i)] <- c( ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$C2.SQ003) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$C2.SQ003),  ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$C2.SQ003) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$C2.SQ003) )[ind]
  
  #climate policy
  df$fly.truth[which(df$respnr==i)] <- c( ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$C1.SQ001) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$C1.SQ001),  ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$C1.SQ001) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$C1.SQ001) )[ind]
  
  df$meat.truth[which(df$respnr==i)] <- c( ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$C1.SQ002) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$C1.SQ002),  ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$C1.SQ002) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$C1.SQ002) )[ind]
  
  df$nature.truth[which(df$respnr==i)] <- c( ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$C1.SQ003) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$C1.SQ003),  ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$C1.SQ003) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$C1.SQ003) )[ind]
  
  #migration
  df$cap.truth[which(df$respnr==i)] <- c( ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$M1.SQ001) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$M1.SQ001),  ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$M1.SQ001) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$M1.SQ001) )[ind]
  
  df$student.truth[which(df$respnr==i)] <- c( ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$M1.SQ002) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$M1.SQ002),  ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$M1.SQ002) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$M1.SQ002) )[ind]
  
  df$threat.truth[which(df$respnr==i)] <- c( ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$M1.SQ003) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_9),]$M1.SQ003),  ifelse( length( alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$M1.SQ003) == 0, NA, alter[which(alter$respnr==i & alter$token==egodata$attribute_10),]$M1.SQ003) )[ind]

}

#based on this, calculate ego's accuracy in positioning alter
#1-(|perception-truth|/range)

#but first, convert positions to numeric
df[,20:length(df)] <- lapply(names(df)[-c(1:19)], function(x) as.numeric(df[[x]]))

{
df$LR.accuracy <- 1-abs(df$LR.perception-df$LR.truth)/11
df$imp_crime.accuracy <- 1-abs(df$imp_crime.perception-df$imp_crime.truth)/4
df$imp_climate.accuracy <- 1-abs(df$imp_climate.perception-df$imp_climate.truth)/4
df$imp_discrim.accuracy <- 1-abs(df$imp_discrim.perception-df$imp_discrim.truth)/4
df$imp_housing.accuracy <- 1-abs(df$imp_housing.perception-df$imp_housing.truth)/4
df$imp_refugee.accuracy <- 1-abs(df$imp_refugee.perception-df$imp_refugee.truth)/4
df$sechand.accuracy <- 1-abs(df$sechand.perception-df$sechand.truth)/4
df$replace.accuracy <- 1-abs(df$replace.perception-df$replace.truth)/4
df$animal.accuracy <- 1-abs(df$animal.perception-df$animal.truth)/4
df$fly.accuracy <- 1-abs(df$fly.perception-df$fly.truth)/4
df$meat.accuracy <- 1-abs(df$meat.perception-df$meat.truth)/4
df$nature.accuracy <- 1-abs(df$nature.perception-df$nature.truth)/4
df$cap.accuracy <- 1-abs(df$cap.perception-df$cap.truth)/4
df$student.accuracy <- 1-abs(df$student.perception-df$student.truth)/4
df$threat.accuracy <- 1-abs(df$threat.perception-df$threat.truth)/4
}

df.ego <- df
rm(df)
#fix(df.ego)
```

<br>


## accuracy from alter's perspective

```{r , eval=F}
#make an (empty) dataframe to store output in, with a row for each alter-ego dyad

df <- data.frame(respnr = alter$respnr,
                 dyad = NA,
                 tie = NA,
                 ego = "alter",
                 
                 #ego characteristics
                 ego_gender = NA,
                 ego_educ = NA,
                 ego_age = NA,
                 
                 #alter
                 alter_gender = NA,
                 alter_educ = NA,
                 alter_age = NA,
                 
                 #sameness
                 same_gender = NA,
                 same_educ = NA,
                 same_age = NA,
                 
                 #networks
                 cdn = NA,
                 study = NA,
                 bff = NA,
                 csn = NA, 
                 
                 #dyad
                 duration = NA,
                 
                 #structure
                 embeddedness = NA,
                 
                 #### opionions ######
                 
                 #left right placement
                 LR.self = NA,
                 LR.perception = NA,
                 LR.truth = NA,
                 LR.accuracy = NA,
                 
                 #importance of political themes
                 imp_crime.self = NA,
                 imp_crime.perception = NA, #crime
                 imp_crime.truth = NA,
                 imp_crime.accuracy = NA,
                 imp_climate.self = NA,
                 imp_climate.perception = NA, #climate
                 imp_climate.truth = NA,
                 imp_climate.accuracy = NA,
                 imp_discrim.self = NA,
                 imp_discrim.perception = NA, #discrimination 
                 imp_discrim.truth = NA,
                 imp_discrim.accuracy = NA,
                 imp_housing.self = NA,
                 imp_housing.perception = NA, #housing shortage
                 imp_housing.truth = NA,
                 imp_housing.accuracy = NA,
                 imp_refugee.self = NA,
                 imp_refugee.perception = NA, #refugees
                 imp_refugee.truth = NA,
                 imp_refugee.accuracy = NA,
          
                 #eco-friendly actions
                 sechand.self = NA,
                 sechand.perception = NA, #buying second hand products
                 sechand.truth = NA,
                 sechand.accuracy = NA,
                 replace.self = NA,
                 replace.perception = NA, #using items as long as possible before replacement
                 replace.truth = NA, 
                 replace.accuracy = NA,
                 animal.self = NA,
                 animal.perception = NA, #reduced consumption of animal products
                 animal.truth = NA, 
                 animal.accuracy = NA, 
                 
                 #climate policy
                 fly.self = NA,
                 fly.perception = NA, #flight tax
                 fly.truth = NA,
                 fly.accuracy = NA,
                 meat.self = NA,
                 meat.perception = NA, #meat tax
                 meat.truth = NA, 
                 meat.accuracy = NA,
                 nature.self = NA,
                 nature.perception = NA, #expandng nature reserves
                 nature.truth = NA, 
                 nature.accuracy = NA, 
                 
                 #migration (policy)
                 cap.self = NA,
                 cap.perception = NA, #annual cap on asylum seekers
                 cap.truth = NA,
                 cap.accuracy = NA,
                 student.self=NA,
                 student.perception = NA, #international students 'enrich' Dutch universities
                 student.truth = NA, 
                 student.accuracy = NA, 
                 threat.self = NA,
                 threat.perception = NA, #migration as a threat to Dutch culture
                 threat.truth = NA, 
                 threat.accuracy = NA)
                 
#reorder
df <- df[order(df$respnr),]
rownames(df) <- 1:nrow(df)

#now, ego characteristics are alter characteristics, and vice versa
gender <- df.ego$ego_gender
gender2 <- df.ego$alter_gender

df$ego_gender <- gender2
df$alter_gender <- gender

#also for age and educ
educ <- df.ego$ego_educ
educ2 <- df.ego$alter_educ

df$ego_educ <- educ2
df$alter_educ <- educ

age <- df.ego$ego_age
age2 <- df.ego$alter_age

df$ego_age <- age2
df$alter_age <- age

# same and duration are similar (symmetric)
df$same_age <- df.ego$same_age
df$same_educ <- df.ego$same_educ
df$same_gender <- df.ego$same_gender
df$duration <- df.ego$duration

#assumption: relation are undirected
df$cdn <- df.ego$cdn
df$study <- df.ego$study
df$bff <- df.ego$bff
df$csn <- df.ego$csn

df$dyad <- df.ego$dyad

for (i in unique(df$respnr)) {
  #unique(df$respnr)[10]->i
   
  #get egodata corresponding to i
  egodata <- ego[which(ego$respnr==i),]
  
  #some double ego-responses (for those who did not complete, but did send the invitation to alters). I take the response that reached the latest page.
  egodata <- egodata[ which(egodata$lastpage == max(egodata$lastpage[!is.na(egodata$lastpage)])), ] 
  
  #get alterdata
  alterdata <- alter[which(alter$respnr==i),]
  
  #give correct order (alter x first, then y)
  alterdata <- alterdata[c(which(alterdata$token==egodata$attribute_9),which(alterdata$token==egodata$attribute_10)),]
  
  df$tie[which(df$respnr==i)] <- as.numeric(paste0(df$dyad[which(df$respnr==i)], "2"))
  
  ### alter's own placement/opinion
  df$LR.self[which(df$respnr==i)] <- as.numeric(stringr::str_extract(alterdata$P1, pattern = "\\(?[0-9,.]+\\)?"))
  df$imp_crime.self[which(df$respnr==i)] <- alterdata$P2.SQ001.
  df$imp_climate.self[which(df$respnr==i)] <- alterdata$P2.SQ002.
  df$imp_discrim.self[which(df$respnr==i)] <- alterdata$P2.SQ003.
  df$imp_housing.self[which(df$respnr==i)] <- alterdata$P2.SQ004.
  df$imp_refugee.self[which(df$respnr==i)] <- alterdata$P2.SQ005.
  df$sechand.self[which(df$respnr==i)] <- alterdata$C2.SQ001.
  df$replace.self[which(df$respnr==i)] <- alterdata$C2.SQ002.
  df$animal.self[which(df$respnr==i)] <- alterdata$C2.SQ003.
  df$fly.self[which(df$respnr==i)] <- alterdata$C1.SQ001.
  df$meat.self[which(df$respnr==i)] <- alterdata$C1.SQ002.
  df$nature.self[which(df$respnr==i)] <- alterdata$C1.SQ003.
  df$cap.self[which(df$respnr==i)] <- alterdata$M1.SQ001.
  df$student.self[which(df$respnr==i)] <- alterdata$M1.SQ002.
  df$threat.self[which(df$respnr==i)] <- alterdata$M1.SQ003.
  
  
  #### alter's perception of ego's position
  
  #LR
  df$LR.perception[which(df$respnr==i)] <- as.numeric(stringr::str_extract(alterdata$P1X, pattern = "\\(?[0-9,.]+\\)?"))
  
  #importance of political topics
  df$imp_crime.perception[which(df$respnr==i)] <- alterdata$P2X.SQ001.
  df$imp_climate.perception[which(df$respnr==i)] <- alterdata$P2X.SQ002.
  df$imp_discrim.perception[which(df$respnr==i)] <- alterdata$P2X.SQ003.
  df$imp_housing.perception[which(df$respnr==i)] <- alterdata$P2X.SQ004.
  df$imp_refugee.perception[which(df$respnr==i)] <- alterdata$P2X.SQ005.

  #eco-friendly behavior
  df$sechand.perception[which(df$respnr==i)] <- alterdata$C2X.SQ001.
  df$replace.perception[which(df$respnr==i)] <- alterdata$C2X.SQ002.
  df$animal.perception[which(df$respnr==i)] <- alterdata$C2X.SQ003.
  
  #climate policy attitude
  df$fly.perception[which(df$respnr==i)] <- alterdata$C1X.SQ001.
  df$meat.perception[which(df$respnr==i)] <- alterdata$C1X.SQ002.
  df$nature.perception[which(df$respnr==i)] <- alterdata$C1X.SQ003.
  
  #migration (policy) attitude
  df$cap.perception[which(df$respnr==i)] <- alterdata$M1X.SQ001.
  df$student.perception[which(df$respnr==i)] <- alterdata$M1X.SQ002.
  df$threat.perception[which(df$respnr==i)] <- alterdata$M1X.SQ003.

  #### where does ego place himself?
  df$LR.truth[which(df$respnr==i)] <- as.numeric(stringr::str_extract(egodata$P1, pattern = "\\(?[0-9,.]+\\)?"))

  #importance of topics
  df$imp_crime.truth[which(df$respnr==i)] <- egodata$P2.SQ001.
  df$imp_climate.truth[which(df$respnr==i)] <- egodata$P2.SQ002.
  df$imp_discrim.truth[which(df$respnr==i)] <- egodata$P2.SQ003.
  df$imp_housing.truth[which(df$respnr==i)] <- egodata$P2.SQ004.
  df$imp_refugee.truth[which(df$respnr==i)] <- egodata$P2.SQ005.
  
  #eco-friendly actions
  df$sechand.truth[which(df$respnr==i)] <- egodata$C2.SQ001.
  df$replace.truth[which(df$respnr==i)] <- egodata$C2.SQ002.
  df$animal.truth[which(df$respnr==i)] <- egodata$C2.SQ003.
  
  #climate policy
  df$fly.truth[which(df$respnr==i)] <- egodata$C1.SQ001.
  df$meat.truth[which(df$respnr==i)] <- egodata$C1.SQ002.
  df$nature.truth[which(df$respnr==i)] <- egodata$C1.SQ003.
  
  #migration
  df$cap.truth[which(df$respnr==i)] <- egodata$M1.SQ001.
  df$student.truth[which(df$respnr==i)] <- egodata$M1.SQ002.
  df$threat.truth[which(df$respnr==i)] <- egodata$M1.SQ003.
}

#based on this, calculate alter's accuracy in positioning ego
#1-(|perception-truth|/range)
#names(df)
#but first, convert positions to numeric
df[,20:length(df)] <- lapply(names(df)[-c(1:19)], function(x) as.numeric(df[[x]]))

{
df$LR.accuracy <- 1-abs(df$LR.perception-df$LR.truth)/11
df$imp_crime.accuracy <- 1-abs(df$imp_crime.perception-df$imp_crime.truth)/4
df$imp_climate.accuracy <- 1-abs(df$imp_climate.perception-df$imp_climate.truth)/4
df$imp_discrim.accuracy <- 1-abs(df$imp_discrim.perception-df$imp_discrim.truth)/4
df$imp_housing.accuracy <- 1-abs(df$imp_housing.perception-df$imp_housing.truth)/4
df$imp_refugee.accuracy <- 1-abs(df$imp_refugee.perception-df$imp_refugee.truth)/4
df$sechand.accuracy <- 1-abs(df$sechand.perception-df$sechand.truth)/4
df$replace.accuracy <- 1-abs(df$replace.perception-df$replace.truth)/4
df$animal.accuracy <- 1-abs(df$animal.perception-df$animal.truth)/4
df$fly.accuracy <- 1-abs(df$fly.perception-df$fly.truth)/4
df$meat.accuracy <- 1-abs(df$meat.perception-df$meat.truth)/4
df$nature.accuracy <- 1-abs(df$nature.perception-df$nature.truth)/4
df$cap.accuracy <- 1-abs(df$cap.perception-df$cap.truth)/4
df$student.accuracy <- 1-abs(df$student.perception-df$student.truth)/4
df$threat.accuracy <- 1-abs(df$threat.perception-df$threat.truth)/4
}

#psych::describe(df[,which(grepl("accuracy", names(df)))])
df.alter <- df
rm(df)
```

<br>

### rbind data-frames

```{r,eval=F}
df.alter$embeddedness <- NA
df <- rbind(df.ego,df.alter)

#reorder by ego id
df <- df[order(df$dyad),]
rownames(df) <- 1:nrow(df)
#fix(df)
``` 

<br>

## save

```{r,eval=F}
fsave(df, "egonets.rda")
```

<br>

# Output

```{r, echo=FALSE}
df <- fload("./data/processed/20250905egonets.Rda")
options(knitr.kable.NA='')

knitr::kable(df, digit=2, "html", caption="Output") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
  kableExtra::scroll_box(width = "100%", height = "300px")

```

----

## References

